---
title: "Homework 5"
subtitle: "Submission 1"
author: Yaseen Bhat
format:
  pdf:
    output-file: "bhat-y-hwk5-1"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
      - \usepackage{hyperref}

---

[Link to Github](https://github.com/yaseen-bhat/homework5)

```{r}
#| include: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stringr, readxl, 
               data.table, gdata, scales, kableExtra, modelsummary, fixest)
```
```{r}
#| include: false
#| eval: true
 
load("/Users/yaseenbhat/Downloads/econ470hw5/submission 1/hw5_workspace.Rdata")
```
\newpage 

\vspace{.2in}
\noindent 1. Plot the share of the adult population with direct purchase health insurance over time. <br>

```{r}
#| echo: false
#| fig-cap: Share of the Adult population with Direct Purchase health insurance over time

print(DirectPurchasePlot)
```

\newpage 

\vspace{.2in}
\noindent 2. Discuss the reduction in direct purchase health insurance in later years. Can you list a couple of policies that might have affected the success of the direct purchase insurance market? <br>

The main policy that impacted the reduction in direct purchase health insurance was a real world event! When the ACA was repealed, there is a direct correlation with a steep drop afterwards.

\newpage 

\vspace{.2in}
\noindent 3. Plot the share of the adult population with Medicaid over time. <br>

```{r}
#| echo: false
#| fig-cap: Share of the Adult population with Medicaid over time

print(medicaid_plot)

```

\newpage 

\vspace{.2in}
\noindent 4. Plot the share of uninsured over time, separately by states that expanded Medicaid in 2014 versus those that did not. Drop all states that expanded after 2014. <br>

```{r}
#| echo: false
#| fig-cap: Share of Uninsured over Time
print(UnInsurancePlot)
```

\newpage 

\vspace{.2in}
\noindent 5. Calculate the average percent of uninsured individuals in 2012 and 2015, separately for expansion and non-expansion states. Present your results in a basic 2x2 DD table. <br>

```{r} 
#| echo: false
#| warning: false
#| tbl-cap: "Uninsured in 2012 and 2015"

print(DiD.tb)
```

\newpage 

\vspace{.2in}
\noindent 6. Estimate the effect of Medicaid expansion on the uninsurance rate using a standard DD regression estimator, again focusing only on states that expanded in 2014 versus those that never expanded. <br>

```{r}
#| echo: false
#| warning: false
#| tbl-cap: Effect of Medicaid Expansion on Uninsurance

modelsummary(DiD.reg1)

```

\newpage 

\vspace{.2in}
\noindent 7. Include state and year fixed effects in your estimates. Try using the lfe or fixest package to estimate this instead of directly including the fixed effects. <br>

```{r}
#| echo: false
#| warning: false


modelsummary(list("DD" = DiD.reg2, "TWFE" = twfe))
```

\newpage 

\vspace{.2in}
\noindent 8. Repeat the analysis in question 7 but include all states (even those that expanded after 2014). Are your results different? If so, why? <br>


```{r}
#| echo: false
#| warning: false

modelsummary(list("DD" = DiD.reg3, "TWFE" = twfe2,"Time Variance" = fe.est2))
```
They are relatively kind of similar, but the new one added all the states as well as time variance. 

\newpage 

\vspace{.2in}
\noindent 9. Provide an “event study” graph showing the effects of Medicaid expansion in each year. Use the specification that includes state and year fixed effects, limited to states that expanded in 2014 or never expanded. <br>

```{r}
#| echo: false
#| fig-cap: Event Study of Medicaid Expansion (2014)

iplot(mod.twfe, 
                   xlab = 'Time to Treatment',
                   main = 'Event Study One')
```

\newpage 

\vspace{.2in}
\noindent 10. Repeat part 9 but again include states that expanded after 2014. Note: this is tricky…you need to put all states onto “event time” to create this graph. <br>


```{r}
#| echo: false
#| fig-cap: Event Study of Medicaid Expansion over Time

iplot(mod.twfe2, 
                     xlab = 'Time to Treatment',
                     main = 'Event Study Two')
```